%-------------------------
% Resume in Latex
% Author : Jake Gutierrez (template)
% Adapted for: Timothy Sorisa
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{iftex}

\ifPDFTeX
  \input{glyphtounicode}
  \pdfgentounicode=1
\fi

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Timothy Sorisa} \\ \vspace{1pt}
    \small \href{mailto:t.sorisa@gmail.com}{\underline{t.sorisa@gmail.com}} \ $|$ \ (863) 256{-}7823 \ $|$ \ United States \ $|$ \
    \href{https://linkedin.com/in/timothy-sorisa-9b650580}{\underline{linkedin.com/in/timothy-sorisa}} \ $|$ \
    \href{https://github.com/tsoris}{\underline{github.com/tsoris}}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Developer}{Oct. 2022 -- Mar. 2024}
      {Amazon Ads}{Santa Monica, CA}
      \resumeItemListStart
        \resumeItem{Developed and maintained full-stack systems using AWS Lambda, SQS, S3, VPC, and CDK to process high-volume ad-shopping data.}
        \resumeItem{Engineered ELT pipelines aggregating millions of records daily, improving ad fund distribution efficiency by 40\%.}
        \resumeItem{Refactored and modernized legacy Java and TypeScript codebases, improving performance and maintainability.}
        \resumeItem{Collaborated with UI/UX Design to enhance TypeScript front-end components, reducing user-flow friction and improving load times.}
        \resumeItem{Implemented automated fail-safes and unit/integration tests to increase reliability and deployment confidence.}
      \resumeItemListEnd

    \resumeSubheading
      {Learning Ambassador}{Dec. 2020 -- Feb. 2022}
      {Amazon Fulfillment}{Lakeland, FL}
      \resumeItemListStart
        \resumeItem{Trained and coached peers in high-volume operations while demonstrating Amazon Leadership Principles.}
        \resumeItem{Admitted into Amazon Technical Academy (competitive internal SDE training program; $<$1\% acceptance rate).}
        \resumeItem{Consistently ranked in the top performance percentile among 100{+} associates through documentation and leadership metrics.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Oregon State University}{Aug. 2025 -- Present}
      {Programming Fundamentals Microcredential}{Remote}
      \resumeItemListStart
        \resumeItem{Maintaining A-level performance in CS 161 (Programming Fundamentals) and CS 225 (Discrete Structures).}
        \resumeItem{Recommended for Undergraduate Learning Assistant (ULA) position based on academic excellence; planning transition into the Post-Baccalaureate Computer Science Program (expected Winter 2026).}
      \resumeItemListEnd

    \resumeSubheading
      {Amazon Technical Academy}{Feb. 2022 -- Oct. 2022}
      {Software Engineering Upskill}{Remote}
      \resumeItemListStart
        \resumeItem{9-month Java-focused software development curriculum covering OOP, data structures, and systems design.}
      \resumeItemListEnd

    \resumeSubheading
      {University of South Florida}{Aug. 2013 -- May 2018}
      {B.S. in Health Sciences}{Tampa, FL}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{AI Email Sorter} $|$ \emph{Python, Gmail API, Supabase, YAML}}{}
      \resumeItemListStart
        \resumeItem{Built a rule-based email classifier integrating AI-assisted sorting and database logging.}
        \resumeItem{Designed modular architecture for future Dockerization and CI/CD pipeline deployment.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Devfolio Website} $|$ \emph{Next.js 15, TypeScript, Tailwind CSS, Framer Motion}}{}
      \resumeItemListStart
        \resumeItem{Developed a responsive portfolio with dynamic hero sections, tooltips, and custom animations.}
        \resumeItem{Deployed on Vercel with GitHub Actions for continuous integration and deployment; integrated Supabase to securely store visitor messages and contact form submissions.}
      \resumeItemListEnd
  \resumeSubHeadingListStart
% (Intentionally using SubHeadingListStart to keep spacing consistent in some template variants)

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, JavaScript, TypeScript, SQL, C++, HTML/CSS} \\
     \textbf{Frameworks \& Tools}{: AWS (Lambda, S3, SQS, VPC, CDK), React, Docker, Git, CI/CD, Unit \& Integration Testing} \\
     \textbf{Concepts}{: Data Structures \& Algorithms, ELT Pipelines, Cloud Architecture, Object-Oriented Design}
    }}
 \end{itemize}

\end{document}

